---
title: "hw12"
author: '111078513'
date: "Help By 108078467"
output:
  pdf_document: 
    includes:
      in_header: "../preamble.tex"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE}
# library("dplyr")
cars <- read.table("auto-data.txt", header=FALSE, na.strings = "?")
names(cars) <- c("mpg", "cylinders", "displacement", "horsepower", "weight", 
                 "acceleration", "model_year", "origin", "car_name")
cars_log <- with(cars, data.frame(log(mpg), log(weight), log(acceleration), 
                                  model_year, origin))
```

# Question 1) Let’s visualize how weight and acceleration are related to mpg.

## a. Let’s visualize how weight might moderate the relationship between acceleration and mpg:

### (i) Create two subsets of your data, one for light-weight cars (less than mean weight) and one for heavy cars (higher than the mean weight)

```{r}
cars_log$weight_mask <- ifelse(cars$weight < mean(cars$weight), 1, 2)
cars_log_light <- cars_log[cars_log$weight_mask == 1, ]
cars_log_heavy <- cars_log[cars_log$weight_mask == 2, ]
```

### (ii) Create a single scatter plot of acceleration vs. mpg, with different colors and/or shapes for light versus heavy cars

```{r}
weight_color = c("blue", "red")
with(cars_log, plot(log.acceleration., log.mpg.,  col=weight_color[weight_mask]))
legend("bottomleft", lty=1, c("light", "heavy"), col=weight_color)
```

### (iii) Draw two slopes of acceleration-vs-mpg over the scatter plot: one slope for light cars and one slope for heavy cars (distinguish them by appearance)

```{r}
cars_log_light_rg <- lm( log.mpg.~ log.acceleration., data=cars_log_light)
cars_log_heavy_rg <- lm(log.mpg.~ log.acceleration., data=cars_log_heavy)
with(cars_log, plot(log.acceleration., log.mpg.,  col=weight_color[weight_mask]))
legend("bottomleft", lty=1, c("light", "heavy"), col=weight_color)
abline(cars_log_light_rg, col = "blue")
abline(cars_log_heavy_rg, col = "red")
```

## b. Report the full summaries of two separate regressions for light and heavy cars where log.mpg. is dependent on log.weight., log.acceleration., model_year and origin

```{r}
cars_log_light_rg_full <- lm( log.mpg.~ log.weight.+ log.acceleration.+ model_year + origin
                              , data=cars_log_light)
summary(cars_log_light_rg_full)
cars_log_heavy_rg_full <- lm( log.mpg.~ log.weight.+ log.acceleration.+ model_year + origin
                              , data=cars_log_heavy)
summary(cars_log_light_rg_full)
```

# Question 2) Use the transformed dataset from above (cars_log), to test whether we have moderation.

## b. Use various regression models to model the possible moderation on log.mpg.: (use log.weight., log.acceleration., model_year and origin as independent variables)

### (i) Report a regression without any interaction terms

```{r}
summary(lm(log.mpg.~log.weight.+log.acceleration.+model_year+factor(origin) 
           , data=cars_log))
```

### (ii) Report a regression with an interaction between weight and acceleration

```{r}
summary(lm(log.mpg.~log.weight.+log.acceleration.+model_year+factor(origin)
           + log.weight.*log.acceleration., data=cars_log))
```

### (iii) Report a regression with a mean-centered interaction term

```{r}
cars_log$log.weight_mc <- scale(cars_log$log.weight., center = T, scale = F) 
cars_log$log.acceleration_mc <- scale(cars_log$log.acceleration., center = T, scale = F)
summary(lm(log.mpg.~ log.weight_mc + log.acceleration_mc + model_year + factor(origin)
           +log.weight_mc * log.acceleration_mc, data=cars_log))
```

### (iv) Report a regression with an orthogonalized interaction term

```{r}
weight_x_acceleration <- cars_log$log.weight. * cars_log$log.acceleration.
interaction_regr <- lm(weight_x_acceleration ~ cars_log$log.weight. 
                       + cars_log$log.acceleration.)
cars_log$interaction_ortho <- interaction_regr$residuals
summary(lm(log.mpg.~log.weight.+log.acceleration.+model_year+factor(origin)
           +interaction_ortho, data=cars_log))
```

## c. For each of the interaction term strategies above (raw, mean-centered, orthogonalized) what is the correlation between that interaction term and the two variables that you multiplied together?

```{r}
correlatin_df <- data.frame()
correlatin_df[1,1] <- with(cars_log, cor(log.weight., log.weight.*log.acceleration.)) 
correlatin_df[2,1] <- with(cars_log, cor(log.acceleration., log.weight.*log.acceleration.))
correlatin_df[1,2] <- with(cars_log, cor(log.weight_mc, log.weight_mc*log.acceleration_mc))
correlatin_df[2,2] <- with(cars_log, cor(log.acceleration_mc, log.weight_mc*log.acceleration_mc))
correlatin_df[1,3] <- with(cars_log, cor(log.weight.,interaction_ortho))
correlatin_df[2,3] <- with(cars_log, cor(log.acceleration.,interaction_ortho))
row.names(correlatin_df) <- c("weight","acceleration") 
colnames(correlatin_df) <- c("raw","mean-centered","orthogonalized") 
print(correlatin_df )
```

# Question 3) We saw earlier that the number of cylinders does not seem to directly influence mpg when car weight is also considered.  But might cylinders have an indirect relationship with mpg through its weight?

## a. Let’s try computing the direct effects first:

### (i) Model 1: Regress log.weight. over log.cylinders. only

```{r}
cars_log2 <- with(cars, data.frame(log(mpg), log(weight),log(cylinders), log(acceleration)
                                   , model_year, origin))
model1 <- lm(log.weight.~log.cylinders., data = cars_log2)
summary(model1)
```

### (ii) Model 2: Regress log.mpg. over log.weight. and all control variables


```{r}
model2 <- lm (log.mpg.~ log.weight.+ log.acceleration.+ model_year+factor(origin)  
              , data=cars_log2)
summary(model2)
```

## b. What is the indirect effect of cylinders on mpg? 

```{r}
model1$coefficients[2]*model2$coefficients[2]
```

## c. Let’s bootstrap for the confidence interval of the indirect effect of cylinders on mpg

### (i) Bootstrap regression models 1 & 2, and compute the indirect effect each time: What is its 95% CI of the indirect effect of log.cylinders. on log.mpg.?

```{r}
boot_mediation <- function(model1,model2,dataset){
  boot_index <- sample(1:nrow(dataset),replace = T) 
  data_boot <- dataset[boot_index,] 
  regr1 <- lm(model1,data_boot)
  regr2 <- lm(model2,data_boot) 
  return(regr1$coefficients[2] * regr2$coefficients[2])
}
indirect <- replicate(2000,boot_mediation(model1,model2,cars_log2)) 
quantile(indirect,probs = c(0.025,0.975))
```

### (iii) Show a density plot of the distribution of the 95% CI of the indirect effect

```{r}
plot(density(indirect),main = "Distribution of the 95% CI of the indirect eff ect")
abline(v=quantile(indirect,probs = c(0.025,0.975)),lty=2,col="red")
```


