---
title: "hw15"
author: '111078513'
date: "Help By 108078467"
output:
  html_document: 
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results = "hide"}
library(seminr)
sec_q <- read.table("security_data_sem.csv", header = TRUE, sep = ",")
```
# Question 1) Composite Path Models using PLS-PM
## a. Create a PLS path model using SEMinR, with all the following characteristics:
### (i) Measurement model – all constructs are measured as composites:
```{r}
sec_q_intxn_mm <- constructs(
  composite("TRUST", multi_items("TRST", 1:4)),
  composite("SEC", multi_items("PSEC", 1:4)), 
  composite("REP", multi_items("PREP", 1:4)), 
  composite("INV", multi_items("PINV", 1:3)), 
  composite("POL", multi_items("PPSS", 1:3)),
  composite("FAML", single_item("FAML1")),
  interaction_term(iv="REP", moderator="POL", method=orthogonal)
)
```
### (ii). Structural Model – paths between constructs as shown in this causal model:
```{r}
sec_q_intxn_sm <- relationships(
  paths(from = c("TRUST", "REP", "INV", "POL", "FAML", "REP*POL"), 
        to = "SEC"), 
  paths(from = "SEC", to = "TRUST")
)
```
## b. Show us the following results in table or figure formats:
### (i) Plot a figure of the estimated model
```{r}
sec_q_intxn_pls <- estimate_pls(data = sec_q,
                               measurement_model = sec_q_intxn_mm, 
                               structural_model = sec_q_intxn_sm) 
plot(sec_q_intxn_pls)
```

### (ii) Weights and loadings of composites

```{r}
sec_q_report <- summary(sec_q_intxn_pls)

# weight
sec_q_report$weights

# loadongs
sec_q_report$loadings
```

### (iii) Regression coefficients of paths between factors

```{r}
sec_q_intxn_pls$path_coef
```

### (iv) Bootstrapped path coefficients: t-values, 95% CI

```{r}
boot_pls <- bootstrap_model(sec_q_intxn_pls, nboot = 100) 
summary(boot_pls)$bootstrapped_total_paths
```

# Question 2) Common-Factor Models using CB-SEM

## a. Create a common factor model using SEMinR, with the following characteristics:

### (i) Either respecify all the constructs as being reflective(), or use the as.reflective() function to convert your earlier measurement model to being entirely reflective.

```{r}
sec_q_intxn_cf_mm <- constructs(
  reflective("TRUST", multi_items("TRST", 1:4)),
  reflective("SEC", multi_items("PSEC", 1:4)), 
  reflective("REP", multi_items("PREP", 1:4)), 
  reflective("INV", multi_items("PINV", 1:3)), 
  reflective("POL", multi_items("PPSS", 1:3)),
  reflective("FAML", single_item("FAML1")),
  interaction_term(iv="REP", moderator="POL", method=orthogonal)
)
```

### (ii) Use the same structural model as before.

```{r}
sec_q_intxn_sm <- relationships(
  paths(from = c("TRUST", "REP", "INV", "POL", "FAML", "REP*POL"), 
        to = "SEC"), 
  paths(from = "SEC", to = "TRUST")
)
sec_q_intxn__cf_pls <- estimate_cbsem( data = sec_q,
                              measurement_model = sec_q_intxn_cf_mm, 
                              structural_model = sec_q_intxn_sm)
```

## b. Show us the following results in table or figure formats

### (i) Plot a figure of the estimated model (it will look different from your PLS model!)

```{r, out.width="50%", fig.align="center"}
plot(sec_q_intxn__cf_pls)
```

### (ii) Loadings of composites

```{r}
sec_q_intxn__cf_pls_report <- summary(sec_q_intxn__cf_pls)
sec_q_intxn__cf_pls_report$loadings
```

### (iii) Regression coefficients of paths between factors, and their p-values

```{r}
sec_q_intxn__cf_pls_report$paths[c("coefficients", "pvalues")]
```