---
title: "HW1"
author: '111078513'
date: "`r Sys.Date()`"
output:
  pdf_document: 
    includes:
      in_header: "preamble.tex"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load customers data

```{r}
data <- read.table("customers.txt", header = T)
age <- data$age
head(age)
```

### 1. What is the 5th element in the original list of ages?

```{r}
q1 <- age[5]
q1
```

### 2. What is the fifth lowest age?
remove the duplicated data from 'age' and get the fifth lowest

```{r}
sort_age <- sort(age)
uni_sort_age <- unique(sort_age)
uni_sort_age[5]
```

### 3. Extract the five lowest ages together

```{r}
head(uni_sort_age, 5)
```

### 4. Get the five highest ages by first sorting them in decreasing order first.

```{r}
tail(uni_sort_age, 5)
```

### 5. What is the average (mean) age?

```{r}
mean(age)
```

### 6. What is the standard deviation of ages?

```{r}
sd(age)
```

### 7. Make a new variable called age_diff, with the difference between each age and the mean age.

```{r}
age_diff <- age - mean(age)
head(age_diff)
```

### 8. What is the average age_diff?

```{r}
mean(age_diff)
```

### 9. Visualize the raw data as we did in class: (a) histogram, (b) density plot, (c) boxplot+stripchart

```{r out.height='100%', fig.align='center'}

# (a) histogram
hist(age)

# (b) density plot
plot(density(age))

# (c) boxplot+stripchart
boxplot(age, horizontal = TRUE)
stripchart(age, method = "stack", add = TRUE)
```

